network_analysis

### 2020-07-13 analyses/network_analysis.Rmd
update repo

### Define functions
#### Rarefied network analysis
```{r, include=FALSE}
# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp_BB <- function(net, n, iter) {

@@

rare_net_sp_FL <- function(net, n, iter) {

@@

  for(i in 1:iter) {
    temp <- net %>%
      dplyr::select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      filter(freq > 1) %>% # remove singletons
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "lower", index = c("d", "species strength", "proportional generality")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "site") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out %>%
    gather(metric, value, -c(sp, site, iteration)) %>% # get mean value across iterations for each metric
    group_by(sp, site, metric) %>%
    summarize(value = mean(value)) %>%
    left_join(site_data) %>%
    left_join(fl_traits, by = c("sp" = "plant.sp"))
}

# network level
rare_net_nt <- function(net, n, iter) {

  for(i in 1:iter) {
    temp <- net %>%
      dplyr::select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, index = c("H2", "weighted NODF", "niche overlap", "C score", "generality", "web asymmetry", "weighted connectance")) %>% # We probably care mainly about the BB level of the network
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(site = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out  %>%
      gather(metric, value, -c(site, iteration)) %>% # get mean value across iterations for each metric
      group_by(site, metric) %>%
      summarize(value = mean(value)) %>%
      left_join(site_data)
}

```

#### Rarefied network analysis by colony phase
```{r, include=FALSE}
# network level version 2
rare_net_nt2 <- function(net, n, iter) {

  t_filter <- net %>%
    dplyr::select(site, date, phase, year) %>%
    unique() %>%
    group_by(site, phase, year) %>%
    mutate(transects = n()) %>%
    filter(transects >= n)

  for(i in 1:iter) {
    temp <- net %>%
      semi_join(t_filter) %>%
      dplyr::select(site, date, phase, year) %>%
      unique() %>%
      group_by(site, phase, year) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, phase, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      #filter(freq > 1) %>%
      unite(webID, c(site, phase, year), sep = "_") %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, level = "higher",
          index = c("web asymmetry", "weighted NODF", "H2", "C score", "niche overlap", "generality")) %>% 
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(id = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out  %>%
      gather(metric, value, -c(id, iteration)) %>% # get mean value across iterations for each metric
      group_by(id, metric) %>%
      summarize(value = mean(value)) %>%
      separate(id, sep = "_", into = c("site", "phase", "year")) %>%
      mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
      left_join(site_data)
}
# species level version 2
rare_net_sp2 <- function(net, n, iter) {

  t_filter <- net %>%
    dplyr::select(site, date, phase, year) %>%
    unique() %>%
    group_by(site, phase, year) %>%
    mutate(transects = n()) %>%
    filter(transects >= n)

  for(i in 1:iter) {
    temp <- net %>%
      semi_join(t_filter) %>%
      dplyr::select(site, date, phase, year) %>%
      unique() %>%
      group_by(site, phase, year) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, phase, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      #filter(freq > 1) %>%
      unite(webID, c(site, phase, year), sep = "_") %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "higher", index = c("d", "species strength")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "id") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out %>%
    gather(metric, value, -c(sp, id, iteration)) %>% # get mean value across iterations for each metric
    group_by(sp, id, metric) %>%
    summarize(value = mean(value)) %>%
    separate(id, sep = "_", into = c("site", "phase", "year")) %>%
    mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
    left_join(site_data) %>%
    left_join(bb_traits, by = c("sp" = "bb.sp"))
}
```

### Rarefied network analysis by floral k.type instead of floral species
```{r}
# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp_k.type.s <- function(net, n, iter) {

  for(i in 1:iter) {
    temp <- net %>%
      dplyr::select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, k.type.s) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      na.omit() %>%
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(k.type.s)) > 1) %>%
      ungroup() %>%
      filter(freq > 1) %>% # remove singletons
      dplyr::select(higher = bb.sp, lower = k.type.s, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "higher", index = c("d", "species strength", "proportional generality")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "site") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out %>%
    gather(metric, value, -c(sp, site, iteration)) %>% # get mean value across iterations for each metric
    group_by(sp, site, metric) %>%
    summarize(value = mean(value)) %>%
    left_join(site_data) %>%
    left_join(bb_traits, by = c("sp" = "bb.sp"))
}

# network level
rare_net_nt_k.type.s <- function(net, n, iter) {

  for(i in 1:iter) {
    temp <- net %>%
      dplyr::select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, k.type.s) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      na.omit() %>%
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(k.type.s)) > 1) %>%
      ungroup() %>%
      dplyr::select(higher = bb.sp, lower = k.type.s, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, level = "higher", index = c("H2", "weighted NODF", "niche overlap", "C score", "generality", "web asymmetry", "weighted connectance")) %>% # We probably care mainly about the BB level of the network
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(site = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

@@

### Load network and survey data
```{r, include=FALSE}
bb_traits <- read_csv("../processed_data/bb_traits.csv") %>%
  dplyr::select(subgenus, bb.sp, pbl.w, pbl.w.class)

fl_traits <- read.csv("../processed_data/floral_k_type_nom_fix.csv") %>%
  dplyr::select(plant.sp, k.type) %>%
  mutate(k.type.s = str_extract(k.type, "[-+]?[0-9]*\\.?[0-9]+"),
         k.type.ss = str_extract(k.type, "[-+]?[0-9]*"))

fl_tax <- read_csv("../processed_data/floral_tax.csv")

breaks <- read_csv("./output/breaks.csv") %>%
  mutate(year = factor(year))

net <- read_csv("../processed_data/network.csv") %>%
  unite(site.year, site, year, sep = "_", remove = FALSE) %>% # create site.year field that can later be split back up
  unite(site.date, site, date, sep = "_", remove = FALSE) %>%
  mutate(year = factor(year)) %>% # convert year to factor
  full_join(bb_traits, by = c("bb.sp" = "bb.sp")) %>%
  left_join(site_data, by = "site") %>%
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(fl_traits) %>%
  left_join(fl_tax, by = "plant.genus") %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)

net_sum <- net %>%
  group_by(site, year, elev.mean, date) %>%
  summarize(total.obs = n()) %>%
  ungroup() %>%
  mutate(elev.fac = factor(elev.mean))

ggplot(net_sum, aes(total.obs)) +
  geom_histogram() +
  facet_grid(elev.fac ~ year)

ggplot(net_sum, aes(total.obs)) +
  geom_histogram() +
  facet_wrap(~year)

survey <- read_csv("../processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  semi_join(net, by = "plant.sp") %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(site_data, by = "site") %>%
  left_join(fl_traits) %>%
  left_join(fl_tax) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```

### Rarefied network analysis (not broken down by phase)
#### Inspect transect counts to set subsampling parameter
```{r, include = FALSE}
### Determine the minimum transect count per site*year to set rarefaction sampling
transects <- net %>%
  dplyr::select(site, year, date) %>%
  unique()

transects_per_siteyear <- transects %>%
  group_by(site, year) %>%
  summarize(transects = n())

min_transects_per_year <- transects_per_siteyear %>%
  group_by(year) %>%
  summarize(min_transects = min(transects))

### Create yearly subsets to feed to rare_net
net_2012 <- filter(net, year == "2012")
# net_2011 <- filter(net, year == "2011")
# net_2010 <- filter(net, year == "2010")

### Demonstrate that the distribution of interaction frequencies does not differ across elevation classes; in other words, no systematic bias is introduced to the network analysis due to uneven frequency of species with few observations
net_freq <- net %>%
  group_by(site, dayofyear, year, bb.sp, elev.mean, elev.class2) %>%
  summarize(freq = n())

ggplot(net_freq, aes(elev.class2, log(freq))) +
  geom_boxplot() +
  facet_wrap(~year)
```

#### Generate network metric tables
```{r, message=FALSE}
### Species level
#### BBs
spmet_2012_BB <- rare_net_sp_BB(net_2012, 9, 40) %>%
  mutate(year = factor(rep("2012", n())))
spmet_2011_BB <- rare_net_sp_BB(net_2011, 4, 40) %>%
  mutate(year = factor(rep("2011", n())))  
spmet_2010_BB <- rare_net_sp_BB(net_2010, 3, 40) %>%
  mutate(year = factor(rep("2010", n())))

spmet_BB <- rare_net_sp_BB(net, 5, 50) %>%
  ungroup() %>%
  mutate(year = factor(year))

@@

spmet_BB <- bind_rows(spmet_2012_BB, spmet_2011_BB, spmet_2010_BB)

#### plants
spmet_2012_FL <- rare_net_sp_FL(net_2012, 9, 40) %>%
  mutate(year = factor(rep("2012", n())))
spmet_2011_FL <- rare_net_sp_FL(net_2011, 4, 40) %>%
  mutate(year = factor(rep("2011", n())))  
spmet_2010_FL <- rare_net_sp_FL(net_2010, 3, 40) %>%
  mutate(year = factor(rep("2010", n())))

spmet_FL <- bind_rows(spmet_2012_FL, spmet_2011_FL, spmet_2010_FL)

spmet_mean_FL <- spmet_FL %>%
  group_by(site, year, elev.mean, metric) %>%
  summarize(value = mean(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(year = factor(year))

### Network- and group-level
netmet_rare_2012 <- rare_net_nt(net_2012, n = 9, iter = 40) %>%
  mutate(year = factor(rep("2012", n())))
netmet_rare_2011 <- rare_net_nt(net_2011, n = 4, iter = 40)  %>%
  mutate(year = factor(rep("2011", n())))
netmet_rare_2010 <- rare_net_nt(net_2010, n = 3, iter = 40) %>%
  mutate(year = factor(rep("2010", n())))

netmet <- bind_rows(netmet_rare_2012, 
                    netmet_rare_2011, 
                    netmet_rare_2010) %>%
  ungroup() %>%
  mutate(metric = factor(metric, levels = c("H2",
                                            "weighted.NODF",
                                            "niche.overlap.HL", 
                                            "C.score.HL",
                                            "generality.HL",
                                            "niche.overlap.LL", 
                                            "C.score.LL",
                                            "generality.LL",
                                            "web.asymmetry",
                                            "weighted.connectance"))) %>%
  mutate(year = factor(year))
```

### Plot network analysis
```{r}
#### Per species values
ggplot(filter(spmet_2012_BB,
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf") & metric == "d"), 
       aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  facet_wrap(~sp, scales = "free")

@@

summary(lm(value ~ elev.mean, data =  filter(spmet_mean_BB, metric == "d" & year == 2012)))
plot(lm(value ~ elev.mean, data =  filter(spmet_mean_BB, metric == "d" & year == 2012)))

##### FL
ggplot(filter(spmet_mean_FL, metric == "d"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("Community mean d'") +
  facet_wrap(~year) +
  theme_light(16)

#### Network level

##### niche overlap
ggplot(filter(netmet, metric == "niche.overlap.HL"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x)) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("Niche overlap") +
  facet_wrap(~year) +
  theme_light(16)

gam_niche.overlap <- gamV(value ~ s(year, bs = "re") + s(elev.mean, by = year, k = 10, bs = "tp", m = 2), 
                         data = filter(netmet, metric == "niche.overlap.HL"),
                         method = "REML")

check.gamViz(gam_niche.overlap)
summary(gam_niche.overlap)

plot(gam_niche.overlap, allTerms = TRUE)

gam_cscore <- gamV(value ~ s(year, bs = "re") + s(elev.mean, by = factor(year), bs = "tp", k = 6, m = 1), 
                  data = filter(netmet, metric == "C.score.HL"),
                  #family = "scat",
                  method = "REML")

check.gamViz(gam_cscore)
summary(gam_cscore)

plot(gam_cscore, allTerms = TRUE)
```

### Rarefied network analysis by k.type instead of by plant sp
```{r, message = FALSE}
### Create yearly subsets to feed to rare_net
net_2012 <- filter(net, year == "2012")
net_2011 <- filter(net, year == "2011")
net_2010 <- filter(net, year == "2010")

### Species level
spmet_2012_k <- rare_net_sp_k.type.s(net_2012, 9, 40) %>%
  mutate(year = factor(rep("2012", n())))
spmet_2011_k <- rare_net_sp_k.type.s(net_2011, 4, 40) %>%
  mutate(year = factor(rep("2011", n())))  
spmet_2010_k <- rare_net_sp_k.type.s(net_2010, 3, 40) %>%
  mutate(year = factor(rep("2010", n())))

spmet_k <- bind_rows(spmet_2012_k, spmet_2011_k, spmet_2010_k)

spmet_mean_k <- spmet_k %>%
  group_by(site, year, elev.mean, metric) %>%
  summarize(value = mean(value))

### Network- and group-level
netmet_rare_2012_k <- rare_net_nt_k.type.s(net_2012, n = 9, iter = 40) %>%
  mutate(year = factor(rep("2012", n())))
netmet_rare_2011_k <- rare_net_nt_k.type.s(net_2011, n = 4, iter = 40)  %>%
  mutate(year = factor(rep("2011", n())))
netmet_rare_2010_k <- rare_net_nt_k.type.s(net_2010, n = 3, iter = 40) %>%
  mutate(year = factor(rep("2010", n())))

netmet_k <- bind_rows(netmet_rare_2012, 
                    netmet_rare_2011, 
                    netmet_rare_2010) %>%
  mutate(metric = factor(metric, levels = c("H2",
                                            "weighted.NODF",
                                            "niche.overlap.HL", 
                                            "C.score.HL",
                                            "generality.HL",
                                            "web.asymmetry",
                                            "weighted.connectance")))
```

# Plot k.type network analysis
```{r}
#### Per species values
ggplot(filter(spmet_2012_k,
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf")), 
       aes(elev.mean, value)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth() +
  facet_grid(metric~sp, scales = "free")

ggplot(filter(spmet_2011_k,
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf")), 
       aes(elev.mean, value)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth() +
  facet_grid(metric~sp, scales = "free")

ggplot(filter(spmet_2010_k,
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf")), 
       aes(elev.mean, value)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth() +
  facet_grid(metric~sp, scales = "free")

#### Community mean d
ggplot(filter(spmet_mean_k, metric == "d"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("Community mean d'") +
  theme_light(16)

ggplot(filter(spmet_mean_k, metric == "d"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("Community mean d'") +
  facet_wrap(~year) +
  theme_light(16)

gam_d <- gam(value ~ year + s(elev.mean, k = 10), 
             data = filter(spmet_k, metric == "d"),
             method = "REML")

gam_d.vis <- getViz(gam_d)
check.gamViz(gam_d.vis)
summary(gam_d.vis)

plot(gam_d.vis, allTerms = TRUE) +
  xlab("Elevation")

#### Network level
ggplot(netmet_k, aes(elev.mean, value)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth() +
  facet_grid(metric~year, scales = "free")

##### H2
ggplot(filter(netmet_k, metric == "H2"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("H2'") +
  theme_light(16)

gam_H2 <- gam(value ~ year + s(elev.mean), 
              data = filter(netmet_k, metric == "H2"),
              method = "REML")

gam_H2.vis <- getViz(gam_H2)
check.gamViz(gam_H2.vis)
summary(gam_H2.vis)

plot(gam_H2.vis, allTerms = TRUE) +
  xlab("Elevation")

##### niche overlap
ggplot(filter(netmet_k, metric == "niche.overlap.HL"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("Niche overlap") +
  theme_light(16)

ggplot(filter(netmet_k, metric == "niche.overlap.HL"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("Niche overlap") +
  facet_wrap(~year) +
  theme_light(16)

gam_niche.overlap <- gam(value ~ year + s(elev.mean), 
                         data = filter(netmet_k, metric == "niche.overlap.HL"),
                         method = "REML")

gam_niche.overlap.vis <- getViz(gam_niche.overlap)
check.gamViz(gam_niche.overlap.vis)
summary(gam_niche.overlap.vis)

plot(gam_niche.overlap.vis, allTerms = TRUE) +
  xlab("Elevation")

##### C.score
ggplot(filter(netmet_k, metric == "C.score.HL"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("C score") +
  theme_light(16)

ggplot(filter(netmet_k, metric == "C.score.HL"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("C score") +
  facet_wrap(~year) +
  theme_light(16)

gam_cscore <- gam(value ~ year + s(elev.mean), 
                  data = filter(netmet_k, metric == "C.score.HL"),
                  method = "REML")

gam_cscore.vis <- getViz(gam_cscore)
check.gamViz(gam_cscore.vis)
summary(gam_cscore.vis)

plot(gam_cscore.vis, allTerms = TRUE) +
  xlab("Elevation")
```

### Do BB species differ in their k.type associations?
```{r}
web_by_site <- net %>%
  group_by(site, bb.sp, k.type.s) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  na.omit() %>%
  group_by(site) %>%
  filter(length(unique(bb.sp)) > 1 & length(unique(k.type.s)) > 1) %>%
  ungroup() %>%
  dplyr::select(higher = bb.sp, lower = k.type.s, webID = site, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

web <- net %>%
  group_by(year, elev.class2, bb.sp, k.type.s) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  na.omit() %>%
  unite(webID, c(year, elev.class2), sep = "_") %>%
  dplyr::select(higher = bb.sp, lower = k.type.s, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

# 2010 high
visweb(web[[1]])
plotweb(web[[1]])

# 2010 low
visweb(web[[2]])
plotweb(web[[2]])

# 2010 med
visweb(web[[3]])
plotweb(web[[3]])

# 2011 high
visweb(web[[4]])
plotweb(web[[4]])

# 2011 low
visweb(web[[5]])
plotweb(web[[5]])

# 2011 med
visweb(web[[6]])
plotweb(web[[6]])

# 2012 high
visweb(web[[7]])
plotweb(web[[7]])

# 2012 low
visweb(web[[8]])
plotweb(web[[8]])

# 2012 med
visweb(web[[9]])
plotweb(web[[9]])

```

### Does tongue length class predict k.type association? Remember that B. wurflenii is primarily a nectar robber.
```{r}
kugler_key <- read_delim("../processed_data/kugler_key.tsv", delim = "\t") %>%
  dplyr::select(1,2)

ggplot(bb_traits, aes(pbl.w)) +
  geom_histogram()

net_cont <- net %>%
  group_by(year, elev.class2, pbl.w.class, k.type.ss) %>%
  summarize(freq = n()) %>%
  group_by(year, elev.class2, pbl.w.class) %>%
  mutate(prop = freq/sum(freq))

net_cont2 <- net %>%
  group_by(year, elev.class2, bb.sp, k.type.ss) %>%
  summarize(freq = n()) %>%
  group_by(year, elev.class2, bb.sp) %>%
  mutate(prop = freq/sum(freq))

ggplot(net_cont, aes(pbl.w.class, freq, fill = k.type.ss)) +
  geom_col() +
  facet_grid(elev.class2 ~ year)

ggplot(net_cont, aes(pbl.w.class, prop, fill = k.type.ss)) +
  geom_col() +
  facet_grid(elev.class2 ~ year)

ggplot(net_cont2, aes(bb.sp, prop, fill = k.type.ss)) +
  geom_col() +
  facet_grid(elev.class2 ~ year)

chisq_mod <- chisq.test(net$pbl.w.class, net$k.type.ss)
chisq_mod

ggplot(net, aes(log(pbl.w), corolla.depth)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)

ggplot(net, aes(dayofyear, corolla.depth)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)

ggplot(net, aes(elev.mean, corolla.depth)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)

ggplot(net, aes(factor(pbl.w.class), corolla.depth)) +
  geom_boxplot() 
```

######## Old analyses that I probably don't care to use but don't want to delete yet #########

>>>>

### Define functions
#### Bootstrapped network analysis: *boot_net* function bootstraps networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
```{r, include=FALSE}
#####################################
######## species level ##############
#####################################
boot_net_sp <- function(net, n, iter) {

@@

#####################################
######## network level ##############
#####################################
boot_net <- function(net, n, iter) {

@@

  for(i in 1:iter) {
    temp <- net %>%
      dplyr::select(site, date) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      group_by(site) %>%
      filter(length(unique(bb.sp)) > 1 & length(unique(plant.sp)) > 1) %>%
      ungroup() %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, level = "higher", weighted = TRUE, 
          index = c("weighted NODF", "niche overlap", 
                    "C score", "generality", "web asymmetry", 
                    "weighted connectance")) %>% # We probably care mainly about the BB level of the network
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(site = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

@@

### Load network and survey data
```{r, include=FALSE}
net <- read_csv("../processed_data/network.csv") %>%
  unite(site.year, site, year, sep = "_", remove = FALSE) %>% # create site.year field that can later be split back up
  mutate(year = factor(year)) %>% # convert year to factor
  left_join(site_data, by = "site") %>%
  left_join(gdd, by = c("site", "date")) %>%
  ungroup() %>%
  arrange(site, date)

# Yearly subsets
net_2012 <- filter(net, year == "2012")
net_2011 <- filter(net, year == "2011")
net_2010 <- filter(net, year == "2010")
```

### Rarefied network analysis (not broken down by phase)
#### Inspect transect counts to set subsampling parameter
```{r, include = FALSE}
### Determine the minimum transect count per site*year to set rarefaction sampling
transects <- net %>%
  dplyr::select(site, year, date) %>%
  unique() %>%
  group_by(site, year) %>%
  summarize(transects = n())

min_transects_per_year <- transects %>%
  group_by(year) %>%
  summarize(min_transects = min(transects))
```

### Network- and group-level metric tables
```{r}
netmet_boot_2012 <- boot_net(net_2012, n = 9, iter = 40) %>%
  mutate(year = factor(rep("2012", n())))
netmet_boot_2011 <- boot_net(net_2011, n = 4, iter = 40)  %>%
  mutate(year = factor(rep("2011", n())))
netmet_boot_2010 <- boot_net(net_2010, n = 3, iter = 40) %>%
  mutate(year = factor(rep("2010", n())))

netmet <- bind_rows(netmet_boot_2012, 
                    netmet_boot_2011, 
                    netmet_boot_2010) %>%
  ungroup() %>%
  mutate(metric = factor(metric, levels = c("weighted.NODF",
                                            "niche.overlap.HL", 
                                            "C.score.HL",
                                            "generality.HL",
                                            "web.asymmetry",
                                            "weighted.connectance"))) %>%
  mutate(year = factor(year),
         site = factor(site))
```

#### Species-level metric tables
```{r, message=FALSE}
### Species level
#### BBs
spmet_2012_BB <- boot_net_sp_BB(net_2012, 9, 40) %>%
  mutate(year = factor(rep("2012", n())))
spmet_2011_BB <- boot_net_sp_BB(net_2011, 4, 40) %>%
  mutate(year = factor(rep("2011", n())))  
spmet_2010_BB <- boot_net_sp_BB(net_2010, 3, 40) %>%
  mutate(year = factor(rep("2010", n())))

spmet_BB <- boot_net_sp_BB(net, 5, 50) %>%
  ungroup() %>%
  mutate(year = factor(year))

@@

spmet_BB <- bind_rows(spmet_2012_BB, spmet_2011_BB, spmet_2010_BB)
```

### Plot network analysis
```{r}
#### Network level
##### niche overlap
ggplot(filter(netmet, metric == "niche.overlap.HL"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x)) +
  #geom_smooth() +
  xlab("Elevation") +
  ylab("Niche overlap") +
  facet_wrap(~year) +
  theme_light(16)

gam_niche.overlap <- gamV(value ~ year + s(site, bs = "re") +
                            s(elev.mean, by = year, k = 10, bs = "tp", m = 2), 
                         data = filter(netmet, metric == "niche.overlap.HL"),
                         method = "REML")

gam_niche.overlap2 <- gamV(value ~ year + s(site, bs = "re") +
                            s(elev.mean, k = 10, bs = "tp", m = 2), 
                         data = filter(netmet, metric == "niche.overlap.HL"),
                         method = "REML")

AIC(gam_niche.overlap, gam_niche.overlap2)

check.gamViz(gam_niche.overlap)
summary(gam_niche.overlap)
print(plot(gam_niche.overlap, allTerms = TRUE), pages = 1)

gam_cscore <- gamV(value ~ year + s(site, bs = "re") + 
                     s(elev.mean, bs = "tp", k = 10, m = 2), 
                  data = filter(netmet, metric == "C.score.HL"),
                  #family = "scat",
                  method = "REML")

check.gamViz(gam_cscore)
summary(gam_cscore)
print(plot(gam_cscore, allTerms = TRUE), pages = 1)

#####################################################################################3

#### Per species values
ggplot(filter(spmet_2012_BB,
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf") & metric == "d"), 
       aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  facet_wrap(~sp, scales = "free")

@@

summary(lm(value ~ elev.mean, data =  filter(spmet_mean_BB, metric == "d" & year == 2012)))
plot(lm(value ~ elev.mean, data =  filter(spmet_mean_BB, metric == "d" & year == 2012)))
```
